### 2013-03-26 doc/sosp13/abstract.tex
edited mods from last night

\Grappa is a runtime system for commodity clusters of multicore computers that
presents a massively parallel, single address space abstraction to
applications. \Grappa's purpose is scalable performance for irregular
parallel applications, such as graph processing. Poor data locality, imbalanced parallel
work and complex communication patterns make these applications difficult to scale.

>>>>

\Grappa is a runtime system for commodity clusters of multicore computers that
presents a massively parallel, single address space abstraction to
applications. \Grappa's purpose is to enable scaling of irregular
parallel applications, such as graph processing. Poor data locality, imbalanced parallel
work and complex communication patterns make scaling these applications difficult.

### 2013-03-26 doc/sosp13/intro.tex
edited mods from last night

\noindent{\bf Low Injection Rate} Reference patterns of irregular
applications are unpredictable, with odds increasing as data is
spread out more broadly across a larger system that a given reference
will refer to memory located remotely.  This behavior constrasts
sharply with that of data-parallel applications for which efficient
frameworks such as MapReduce~\cite{mapreduce:osdi04} may exploit the
structure of computation and data affinity to limit internode
communication to comparably infrequent and larger messages.  Mass
market network technology is designed to transfer these larger blocks
of data, not the word-sized references emitted by irregular
application tasks. Injection rate into the network is insufficient to
utilize wire bandwidth when blocks are below about two-kilobytes, so
any naive communication strategy severely under-utilizes the network.

\noindent{\bf High Latency} Unlike data parallel applications, whose
communications are regular and expected, and can therefore easily be
overlapped with computation at the application level, irregular
application tasks encounter remote references throughout their execution
and must resolve them before making further progress.  The latency of
commodity networks is anywhere from a one to hundreds of microseconds,
far more than can be tolerated via the simultaneous multithreading
available in x86 processors.  Consequently, even with RDMA, processor
prefetching and caching hardware alone is inadequate to ensure pipeline
utilization in the presence of high latency networks.

>>>>

\noindent{\bf Low Injection Rate} Reference patterns of irregular
applications are unpredictable, with odds increasing as data is
spread out more broadly across a larger system that a given reference
will refer to memory located remotely.  This behavior constrasts
sharply with that of data-parallel applications for which efficient
frameworks such as MapReduce~\cite{mapreduce:osdi04} may exploit the
structure of computation and data affinity to limit internode
communication to less infrequent, larger messages.  Mass
market network technology is designed to transfer these larger blocks
of data, not the word-sized references emitted by irregular
application tasks. Injection rate into the network is insufficient to
utilize wire bandwidth when blocks are below about two-kilobytes, so
any naive communication strategy severely under-utilizes the network.

\noindent{\bf High Latency} To tolerate latency, data parallel applications make explicit
their regular, predictable communications so as to minimize interference with computation.
In contrast, irregular application tasks encounter remote references dynamically during
execution and must resolve them before making further progress.  The latency of
commodity networks is anywhere from one to hundreds of microseconds,
far more than can be tolerated via the hyperthrading available in x86 processors.
Consequently, even with RDMA, processor prefetching and caching hardware alone is inadequate
to ensure pipeline utilization in the presence of high latency networks.
